
\documentclass[line,margin,hidelinks]{res}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{amsmath}
\hypersetup{colorlinks=true,
  urlcolor=blue,
  pdfauthor={Shawn F. Murphy},
  pdftitle={CV of Shawn F. Murphy},
  pdfsubject={smurp}}
% TODO get pdfpagemode=UseOutlines to work by extending res.cls

%% \pagestyle{fancy}
%% \fancyhead{}
%%\fancyfoot{}
%% \fancyfoot[L] {\thepage}

\topmargin=-0.5in % start text higher on the page
\font\attand=cmr7

\input{globals.tex}

\begin{document}


\name{Shawn F. Murphy}
\input{section/address.tex}

\resumewidth=7in
\begin{resume}

\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Profile:
  \newline \newline
  \maybemugshot
  \footnotesize{\textit{see} \href{\resUrl}{1 pg resume}}
}
\input{section/profile.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Specialties:}
\begin{ncolumn}{2}
$\bullet$ Knowledge Representation / Graphs
 &$\bullet$ Semantic Web\\
$\bullet$ Distributed Systems
 &$\bullet$ Collaborative Filtering\\
$\bullet$ Extreme Programming / Agile
 &$\bullet$ Relational Databases\\
$\bullet$ Electronic Data Interchange
 &$\bullet$ Object Relational Mapping\\
$\bullet$ Functional Programming
 &$\bullet$ Object Oriented Programming\\
$\bullet$ Cognitive Computing
 &$\bullet$ Dynamic Graphics\\
%$\bullet$ Asynchronous Web Servers
% &$\bullet$ Pattern Languages\\
$\bullet$ Data, Context, Interaction
  &$\bullet$ Browser Extensions\\
%$\bullet$ Identity Management
% &$\bullet$ NoSQL Datastores\\
$\bullet$ DevOps
 &$\bullet$ Open Source / Free Software\\

\end{ncolumn}

\section{Languages, Formats, APIs and DTDs:}
\input{languages.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Standards Implemented:}
\begin{ncolumn}{5}

 $\bullet$ TMDM
 &$\bullet$ OKBC
 &$\bullet$ RETS\\
 $\bullet$ Digest Auth
 &$\bullet$ RBAC
 &$\bullet$~ANSI~X12~EDI\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systems:}
\begin{ncolumn}{6}
  $\bullet$ Linux
 &$\bullet$ OS X
 &$\bullet$ iOS
 &$\bullet$ Android\\
  $\bullet$ AS/400
 &$\bullet$ NeXTstep
  &$\bullet$ Windows
  &$\bullet$ AppleII\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software:}
\begin{ncolumn}{5}
$\bullet$ Emacs
 &$\bullet$ OrgMode
 &$\bullet$ GIT
 &$\bullet$ Eclipse
 &$\bullet$ VirtualBox\\

$\bullet$ SQLite
 &$\bullet$ MongoDB
 &$\bullet$ Oracle
 &$\bullet$ MySQL
 &$\bullet$ PostgreSQL\\

$\bullet$ Django
 &$\bullet$ Flask
 &$\bullet$ Medusa
 &$\bullet$ Zope
 &$\bullet$ Express\\

$\bullet$ GIMP
 &$\bullet$ Docker
 &$\bullet$ POVRay
 &$\bullet$ Squeak
 &$\bullet$ \footnotesize{Google Workspace}\\

$\bullet$ NodeJS
 &$\bullet$ SalesForce
 &$\bullet$ OpenSCAD
 &$\bullet$ GraphViz
 &$\bullet$ \small{ElasticSearch}\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Industries:}
\begin{ncolumn}{2}
$\bullet$ Molecular Nanotechnology
 &$\bullet$ Bioinformatics\\
$\bullet$ Bibliographic Systems
 &$\bullet$ Digital Humanities\\
$\bullet$ B2B \& B2C E-Commerce
 &$\bullet$ Database Publishing\\
$\bullet$ Real Estate
 &$\bullet$ Recruiting Systems\\
$\bullet$ Fleet Automation \& Tracking
 &$\bullet$ Supply Chain Automation\\
$\bullet$ Laboratory Information Management
 &$\bullet$ Learning Management\\
\end{ncolumn}


\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/nooron_inc.tex}
\begin{position}
Nooron is a long-term R\&D project in pursuit of exponentiating
collective human cognition.  It consists of a novel semantic database
backend and flexible frontend which includes knowledge management,
data visualization and collective intelligence application development
tools.  Shawn leads this six person company and also serves as
software architect and lead programmer.  Nooron Inc is funded by
angel investment; management services to consumer products vendors;
and semantic software development services to Universities including
Guelph, Alberta, Cambridge and Exeter.
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/connectifier.tex}
\begin{position}
Used Java, Scala, AngularJS, the Play Framework, MongoDB, Elastic
Search and Selenium as part of a startup team to build a category
leading recruiting platform.  Connectifier used big data and machine
learning techniques to crawl the web and social networks for CV and
contact information to empower recruiters specialized in hiring
software engineering talent.  Shawn was their sixth engineer following
the four initial Google software engineers.  Shawn left to found Nooron
Collaboratory.  Connectifier was later acquired by LinkedIn.
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/orlando.tex}
\begin{position}
Coding and architecting an animated highly interactive semantic
visualization research platform using D3, Canvas, RDF and NodeJS for a
university consortium working in the digial humanities.  It features
multi-modal interactivity ( using direct manipulation; bulk
specification and a novel semantic graph layout specification language
) to support visual exploration of a large text corpus.
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/semandra.tex}
\begin{position}
Semandra provided full-service front-to-backend
website development specializing in graphics-intensive designs with
multimedia integration, database-driven backends with complex
programming requirements, and content-rich user-maintainable CMS
sites.

\begin{itemize}
  \item Ponderate --- an agile, collective knowledge curation and evaluation tool
  \item TOBFleet --- a RESTful web service which simplifies vehicle fleet integrations
  \item Theamatic --- a web application for repertory theatre and film
    festival management.
  \item CReturns --- a graphical scheduling system, e-commerce
    solution and SalesForce integration for this home energy auditing and
    retrofitting service
\end{itemize}
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/smurp_com.tex}
\begin{position}
Smurp.com provided contract programming and consulting services with a focus
on database-backed web sites and complex data processing operations.

\begin{itemize}
%  \item Nooron --- an experimental knowledge publishing and collaboration
%    environment featuring knowledge-based web-apps such as:
%    project management, pattern languages, blogging and FAQs.
%    It published knowledge within and about itself in various textual
%    and graphical forms:
%    DocBook, Rich Text, SVG, GIF, JPG, PDF and Postscript;
%    UML diagrams; state-transition diagrams; network graphs;
%    inheritance trees and PERT charts.

  \item PyOKBC --- A Python implementation of the
     \emph{Open KnowledgeBase Connectivity}
  system of knowledge representation and abstraction.
  It was designed to provide a single consistent interface to diverse structured
  information sources, to include ontologies, relational databases,
  xml documents, and topic maps. % PyOKBC was Free Software under the LGPL.

  \item PyRETS --- An implementation of the \emph{Real Estate Transaction System}
  for keeping the Vancouver Real Estate Board synchronized with MLS.ca

  \item CatPub --- A database publishing technology consisting of a
  \PS templating system over a relational database back-end.
  Suitable for automatically preparing complex, highly customized,
  \PS and PDF publications such as directories and catalogs,
  it is closed source software created under contract for a firm
  providing publishing services to the real estate industry.
  It is producing on the order of 10 thousand unique catalog pages
  every day containing constantly changing data for the largest
  real estate boards in Western Canada.

  \item TKQ2.0 --- A Django e-store system vending e-books for hundreds
  of educational publishers, through a dozen store-fronts, with sophisticated
  features such as promotions, steganographic watermarking in PDF, bundling,
  coupons and more.

  \item TKQW --- A Medusa-based ``digital drop-shipping`` system
  enabling digital goods sale and delivery by untrusted 3rd parties.

  \item ModelViz --- Added dynamic SVG-based touring facilities to this Django
  model entity-relationship visualizer.

  \item Alberta Lodging Association --- A Django-based lodgings database
  backing a web site, a printed directory and an associated advertising
  sales and layout system.

\end{itemize}
\end{position}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/emergence_com.tex}
\begin{position}
  Shawn founded Emergence by Design along with four colleagues to pursue
  the development of \emph{The Idea Engine}.  To fund the ongoing development of
  TIE, Shawn led EbD to become a dot-com factory, providing consulting,
  development, hosting and e-commerce services to new dot-com ventures.
  Shawn was Chairman, VP of R\&D, lead developer and chief architect of this
  15-person organization, until selling his interest in 2003.

\begin{itemize}

\item TheIdeaEngine --- architect and lead developer of this R\&D project
  developing a distributed knowledge representation system using
  Java (and JDBC), Perl (and DBI), Scheme, and various SQL backends.
  The effort included the
  implementation of the OKBC (Open Knowledge Base Connectivity)
  specification in Java and Perl,
  the authoring of a multithreaded knowledge server
  and the creation of many perl CGIs, Java Applets and Applications.

\item \href{https://web.archive.org/web/20140517102110/http://getcited.org/}{GetCited.org}
  --- chief architect and lead developer on this massive, highly abstracted
      academic bibliographic portal system featuring:
  \begin{itemize}
    \item reference and citation cross-references
    \item per-publication discusion forums
    \item curriculum vitae management
    \item links with Amazon and other vendors for associate
    referral income
    \item seeded with MARC Book and Serials databases from Library of Congress
    \item rich array of publication types (proceedings, books, articles,
       manuscripts, bibliographies, etc)
    \item tracking of individual/institutional affiliations
    \item sophisticated statistics on publishing influence of
       nations, institutions and individuals based on citation counts
  \end{itemize}

\item \href{https://web.archive.org/web/20130302232056/http://www.dedicatedteacher.com/}{DedicatedTeacher.com}
   --- architect and lead developer
  for this large, highly abstracted e-commerce engine featuring:
    \begin{itemize}
      \item sells both 'digital-goods' (eg. MP3s and PDFs of books)
      and 'tangible goods' (printed books, CDs, educational kits)
      \item complex shipping options
      \item multiple suppliers per store
      \item sophisticated coupon, bundle, sale and promotion features
      \item serves store fronts for various companies
      (e.g. Scholastic)
      \item supports multiple currencies, multiple credit-card
      transaction backends simultaneously and selectively
      (depending on currency, card-type, availability, etc.)
    \end{itemize}

\item \href{https://web.archive.org/web/19991205174419/http://www.lawopinion.com/}{Law Opinion}
   --- architect and developer of the worlds first E-Commerce facility for
       the provision of paid legal opinions.
       It included numerous encryption safeguards
       to ensure complete client confidentiality; a
       system for letting people pick the nearest
       lawyer with experience in the chosen area of
       the law;  and a sophisticated, dynamic,
       system for performing branching automated interviews.
\item \href{http://findamentor.com/}{FindAMentor.com}
   --- architect and lead developer of this system
       for helping people find and interact with mentors in
       various areas of their lives; complete with anonymization and
       multiple personal profiles in different areas of interest
\item EmailDirector
   --- architect and developer of this school management
       system with parallel web and email interfaces
       and sophisticated email transaction system for,
       at that time, Canada's largest e-school
       with 2500 grade-school students
\item EStore
   --- architect and developer of this web interface for creating E-Commerce
       websites using NGage Electronic Commerce technology
\item recruiter matchmaking system
   --- salvaged, re-architected and built out a head-hunting firm's
       matchmaking system for staffing high-tech jobs based on skill, locality
       and position type
\item ClickTrace --- architect and developer of this web log mining facility
\item Domainatrix --- architect and developer of this
                      toolset for bulk management of domain registrations,
                      DNS configurations and network interface
                      configuration
\item Edmonton Chamber of Commerce Annual Directory ---
         architect of this database-driven directory
         including ads and equivalents of white pages and yellow pages
\item magazine publishing system ---
  architect of this complete publishing solution
  with extensive features for advertising sales management and ad layout
  automation

\end{itemize}

\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/govt_alberta.tex}
\begin{position}
  Shawn was responsible for analysis, design, programming,
  training and support of LABBASE: a multi-disciplinary LIMS
  (Laboratory Information Management System) coded in Paradox and
  WordBasic.  It co-operated with a legacy AS/400 appliction written
  in RPG/400 and CL, which he also maintained.  During this project he
  managed three other programmers, the AS/400 administrator and a tech
  support person.
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/sapient.tex}
\begin{position}
Sapient Systems specialized in the creation of desktop database apps.
\begin{itemize}
\item Wrote {\it FastEDI} in PAL (the Paradox Application Language)  to
	provide a subset of the
	ANSI X.12 (V3.020) Electronic Data Interchange system for an
	oilfield supply company interested in easing the ordering process for
	the many regional offices of their large clients in the oil patch.
	{\it FastEDI v1.0} implemented
	the transaction sets for Price/Sales Catalog (832) and
	Purchase Order (850) thus enabling the electronic distribution
	of the latest pricelist and placement of orders.
\item Created a {\it Disability Inventory \& Assessment System }
	for an Educational Consultant to use as a proof of concept of
	her doctoral work for possible productization.
\item Created a {\it Property Management System} for a Realty Firm to
	track the features, locations, prices and owners of
	available commercial real estate to facilitate showing to clients
\item Attended ``NeXT Developer Camp`` and wrote \emph{Elements.app}
\end{itemize}
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{jobs/technowatch.tex}
\begin{position}
  Founded and managed this non-profit think tank focused on the existential
  risks of emerging technologies such as nanotech, biotech, AI and robotics.
  Put on presentations, guided staff, and conducted a scientific literature review.
\end{position}


% \title{ Programmer }
% \location{ Edmonton, AB}
% \employer{Dept of Fish \& Wildlife}
% \dates{Fall 1989}
% \begin{position}
% Developed software to track and order laboratory supplies.
% \end{position}

%\input{jobs/rts.tex}
%\begin{position}
%Various programming, consulting and training projects
%including:
% \begin{itemize}
% \item Programmed Hotel Guest Information System
% \item BBS \& Network for an International Development Organization
% \end{itemize}
%\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{edu/all.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section/interests.tex}

\end{resume}
\end{document}
