rather
\documentclass[line,margin]{res}
\usepackage{verbatim}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
  urlcolor=blue,
  hidelinks=true,
  pdfauthor={Shawn F. Murphy},
  pdftitle={Resume of Shawn F. Murphy},
  pdfsubject={smurp}}
% TODO get pdfpagemode=UseOutlines to work by extending res.cls

\topmargin=-0.5in % start text higher on the page
\font\attand=cmr7

%
% Logos
% =====
\def\PS{{\tt P\small OST\tt S\small CRIPT}}
\def\ATT{{AT{\attand \&}T}}
\def\MF{{METAFONT}}
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\AmSTeX{{$\cal A\kern-.1667em\lower.5ex\hbox{$\cal M$}\kern-.125em
S$-\TeX}}

\begin{document}


\name{Shawn F. Murphy}
 \address{\url{http://smurp.com}\\ Berlin\\
   % \href{callto:+17809032428}{(780) 903-2428}\\
 \href{callto:+491625808994}{+491625808994}\\
  {\tt \href{mailto:smurp@smurp.com}{smurp@smurp.com}}}

\resumewidth=7in
\textheight=10.2in
\begin{resume}

\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction:}
\begin{par}

I am a software architect, knowledge engineer,
software developer, development team leader, programming coach
and trainer -- with 28 years professional experience.
I design and build large data-driven, scientific, academic,
collaborative, e-commerce, publishing systems and frameworks.
I am fluent in diverse programming languages, knowledge
representation technologies, frameworks, visualization tools, RDBMSes,
ORMs, APIs, standards, methodologies and architectural styles.

\begin{comment}
Examples of my work include:
  a vehicle fleet tracking system with RESTful API;
  multiple dynamic knowledge visualization systems;
  a custom database publishing system used by the largest real estate
    markets in Western Canada;
  real-estate systems powered by his own RETS implementation;
  a large bibliographic collaboration system seeded with Library of Congress data;
  a Laboratory Information Management System for disease diagnosis which
    captured, processed and reported on disparate scientific data streams;
  recruiting management systems;
  numerous B2B and B2C e-commerce technologies and systems
    (handling both digital and tangible goods);
  and many other projects involving sophisticated data-sets and processing.
\end{comment}

My current work is  is focused
on exploiting knowledge representation, collaborative filtering, evolutionary
pressure and mass customization strategies for building out a global-scale
knowledge management eco-system wherein software, knowledge and presentation
co-evolve under the pressure of human opinion.

\end{par}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Specialties:}
\begin{ncolumn}{2}
$\bullet$ Knowledge Representation
 &$\bullet$ Semantic Web\\
$\bullet$ Knowledge Publishing
 &$\bullet$ Collaborative Filtering\\
%$\bullet$ Extreme Programming
% &$\bullet$ Relational Databases\\
$\bullet$ Electronic Data Interchange
 &$\bullet$ E-Commerce\\
$\bullet$ Open Source / Free Software
 &$\bullet$ Object Oriented Programming\\
$\bullet$ Test Driven Development
 &$\bullet$ Dynamic Graphics\\
$\bullet$ Asynchronous Web Servers
 &$\bullet$ Pattern Languages\\
$\bullet$ Object Relational Mapping
 &$\bullet$ Topic Maps\\
$\bullet$ Identity Management
 &$\bullet$ NoSQL Datastores\\

\end{ncolumn}

\section{Languages, Formats, APIs and DTDs:}
\input{langauges_formats_apis_and_dtds.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Standards Implemented:}
\begin{ncolumn}{5}

 $\bullet$ TMDM
 &$\bullet$ OKBC
 &$\bullet$ RETS\\
 $\bullet$ Digest Auth
 &$\bullet$ RBAC
 &$\bullet$~ANSI~X12~EDI\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systems:}
\begin{ncolumn}{6}
  $\bullet$ Linux
 &$\bullet$ OS X
 &$\bullet$ iOS
 &$\bullet$ Android\\
  $\bullet$ AS/400
 &$\bullet$ NeXTstep
 &$\bullet$ Windows\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software:}
\begin{ncolumn}{5}
$\bullet$ Emacs
 &$\bullet$ Bazaar
 &$\bullet$ GIT
 &$\bullet$ Eclipse
 &$\bullet$ VirtualBox\\

$\bullet$ SQLite
 &$\bullet$ MongoDB
 &$\bullet$ Oracle
 &$\bullet$ MySQL
 &$\bullet$ PostgreSQL\\

$\bullet$ Django
 &$\bullet$ Tornado
 &$\bullet$ Medusa
 &$\bullet$ Zope
 &$\bullet$ \footnotesize{PlayFramework}\\

$\bullet$ GIMP
 &$\bullet$ OpenOffice
 &$\bullet$ POVRay
 &$\bullet$ Squeak
 &$\bullet$ Singly\\

$\bullet$ NodeJS
 &$\bullet$ SalesForce
 &$\bullet$ BeanStream
 &$\bullet$ GraphViz
 &$\bullet$ \small{ElasticSearch}\\
\end{ncolumn}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Industries:}
\begin{ncolumn}{2}
$\bullet$  Bibliographic Systems
 &$\bullet$ Digital Humanities\\
$\bullet$ B2B \& B2C E-Commerce
 &$\bullet$ Database Publishing\\
$\bullet$ Real Estate
 &$\bullet$ Recruiting Systems\\
$\bullet$ Fleet Automation \& Tracking
 &$\bullet$ Supply Chain Automation\\
$\bullet$ Laboratory Information Management
 &$\bullet$ Learning Management\\
\end{ncolumn}


\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience:}

\title{ Founder \& CEO }
\location{ Edmonton, Canada }
\employer{ \href{http://nooron.com}{Nooron Collaboratory Inc} }
\dates{2015 to present}
\begin{position}
  I am the founder and software architect of Nooron:
  a web-based productivity suite, decision support and collective human cognition platform.
  It consists of a novel semantic database backend and flexible frontend which includes knowledge
  management, data visualization and collective intelligence application development tools.
  Nooron Inc is funded both by angel investment and by revenue from services delivered to
  a consortium of universities including the University of Guelph, the University of Alberta
  and Cambridge University.
\end{position}

\title{ Fullstack Software Engineer }
\location{ Orange County, California }
\employer{ \href{http://connectifier.com}{Connectifier} }
\dates{2013 to 2014}
\begin{position}
  I used Java, Scala, AngularJS, the Play Framework, MongoDB, Elastic Search and Selenium
  as part of a startup team to build a category leading recruiting platform.
  Connectifier uses big data and machine learning techniques to crawl the web and social
  networks for CV and contact information to empower recruiters specialized in hiring
  software engineering talent.
  I was engineer \#6 after the four initial Google software engineers.
  I left to found Nooron Collaboratory.
  Connectifier was later acquired by LinkedIn.
\end{position}

\title{ Architect \& Programmer }
\employer{ \href{https://www.artsrn.ualberta.ca/orlando/}{The Orlando Project} }
\location {Universities of Alberta, Guelph \& McGill}
\dates{2013 to 2014}
\begin{position}
  I architected and coded an animated highly interactive semantic visualization research platform using
  D3, Canvas, RDF, OWL, XML and NodeJS for a university consortium working in the digial humanities.
  It features multi-modal interactivity ( using direct manipulation; bulk specification
  and a novel semantic graph layout specification language ) to support visual exploration of a
  large text corpus.
\end{position}

\title{ Founder, CTO, Software Architect }
\location{ Edmonton, Canada}
\employer{ \href{http://semandra.com}{Semandra, Inc.} }
\dates{2011 to 2014}
\begin{position}
  Semandra provided full-service front-to-backend
  website development specializing in graphics-intensive designs with
  multimedia integration, database-driven backends with complex
  programming requirements, and content-rich user-maintainable CMS
  sites.

\begin{itemize}
  \item Ponderate --- an agile, collective knowledge curation and evaluation tool
  \item TOBFleet --- a RESTful web service which simplifies vehicle fleet integrations
  \item Theamatic --- a web application for repertory theatre and film
    festival management.
  \item CReturns --- a graphical scheduling system, e-commerce
    solution and SalesForce integration for this home energy auditing and
    retrofitting service
\end{itemize}

\end{position}


\title{ Principal }
\location{Edmonton, Canada}
\employer{ \href{http://smurp.com}{smurp.com} }
\dates{2002 to 2011}

\begin{position}
  Smurp.com provided contract programming and consulting services with a focus
  on database-backed web sites and complex data processing operations.

\begin{itemize}
%  \item Nooron --- an experimental knowledge publishing and collaboration
%    environment featuring knowledge-based web-apps such as:
%    project management, pattern languages, blogging and FAQs.
%    It published knowledge within and about itself in various textual
%    and graphical forms:
%    DocBook, Rich Text, SVG, GIF, JPG, PDF and Postscript;
%    UML diagrams; state-transition diagrams; network graphs;
%    inheritance trees and PERT charts.

  \item PyOKBC --- A Python implementation of the
     \emph{Open KnowledgeBase Connectivity}
  system of knowledge representation and abstraction.
  It was designed to provide a single consistent interface to diverse structured
  information sources, to include ontologies, relational databases,
  xml documents, and topic maps. % PyOKBC was Free Software under the LGPL.

  \item PyRETS --- An implementation of the \emph{Real Estate Transaction System}
  for keeping the Vancouver Real Estate Board synchronized with MLS.ca

  \item CatPub --- A database publishing technology consisting of a
  Postscript templating system over a relational database back-end.
  Suitable for automatically preparing complex, highly customized,
  Postscript and PDF publications such as directories and catalogs.
  It continues to drive print automation for the largest real estate
  markets in British Columbia.

  \item TKQ2.0 --- A Django e-store system vending e-books for hundreds
  of educational publishers, through a dozen store-fronts, with sophisticated
  features such as promotions, steganographic watermarking in PDF, bundling,
  coupons and more.

  \item TKQW --- A Medusa-based ``digital drop-shipping`` system
  enabling digital goods sale and delivery by untrusted 3rd parties.

  \item ModelViz --- Added dynamic SVG-based touring facilities to this Django
  model entity-relationship visualizer.

  \item Alberta Lodging Association --- A Django-based lodgings database
  backing a web site, a printed directory and an associated advertising
  sales and layout system.

\end{itemize}

\end{position}



\title{ Founder, Chairman and VP, R\&D }
\location{Edmonton, Canada}
\employer{ \href{http://emergence.com}{Emergence by Design, Inc.} }
\dates{Oct 1995 to Jan 2003}

\begin{position}
  I founded Emergence by Design and acted as
  VP of R\&D, lead developer and chief architect of this 15-person
  software development organization.
  Emergence by Design provided consulting, development, hosting and
  ecommerce services to new dot-com ventures.

\begin{itemize}

\item \href{https://web.archive.org/web/20140517102110/http://getcited.org/}{GetCited.org}
  --- chief architect and lead developer on this massive, highly abstracted
      academic bibliographic portal system featuring:
  \begin{itemize}
    \item reference and citation cross-references
    \item per-publication discusion forums
    \item curriculum vitae management
    \item links with Amazon and other vendors for associate
    referral income
    \item seeded with MARC Book and Serials databases from Library of Congress
    \item rich array of publication types (proceedings, books, articles,
       manuscripts, bibliographies, etc)
    \item tracking of individual/institutional affiliations
    \item sophisticated statistics on publishing influence of
       nations, institutions and individuals based on citation counts
  \end{itemize}

\item \href{http://www.dedicatedteacher.com/}{DedicatedTeacher.com}
   --- architect and lead developer
  for this large, highly abstracted ecommerce engine featuring:
    \begin{itemize}
      \item sells both 'digital-goods' (eg. MP3s and PDFs of books)
      and 'tangible goods' (printed books, CDs, educational kits)
      \item complex shipping options
      \item multiple suppliers per store
      \item sophisticated coupon, bundle, sale and promotion features
      \item serves store fronts for various companies
      (e.g. Scholastic)
      \item supports multiple currencies, multiple credit-card
      transaction backends simultaneously and selectively
      (depending on currency, card-type, availability, etc.)
    \end{itemize}

\item \href{https://web.archive.org/web/19991205174419/http://www.lawopinion.com/}{Law Opinion}
   --- architect and developer of the worlds first E-Commerce facility for
       the provision of paid legal opinions.
       It included numerous encryption safeguards
       to ensure complete client confidentiality; a
       system for letting people pick the nearest
       lawyer with experience in the chosen area of
       the law;  and a sophisticated, dynamic,
       system for performing branching automated interviews.
\item \href{http://findamentor.com/}{FindAMentor.com}
   --- architect and lead developer of this system
       for helping people find and interact with mentors in
       various areas of their lives; complete with anonymization and
        multiple personal profiles in different areas of interest
\item EmailDirector
   --- architect and developer of this web-based school management
       system with parallel web and email interfaces
       and sophisticated email transaction system for,
       at that time, Canada's largest e-school
       with 2500 grade-school students
\item EStore
   --- architect and developer of this web interface for creating E-Commerce
       websites using NGage Electronic Commerce technology
\item ClickTrace --- architect and developer of this web log mining facility
\item Domainatrix --- architect and developer of this
                      toolset for bulk management of domain registrations,
                      DNS configurations and network interface
                      configuration
\item Edmonton Chamber of Commerce Annual Directory ---
         architect of this database-driven directory
         including ads and equivalents of white pages and yellow pages

\end{itemize}

\end{position}



\title{Systems Analyst III}
\location{ Edmonton, Canada}
\dates{1990 to 1995}
\employer{Gov't of Alberta}
\begin{position}
  I was responsible for analysis, design, programming, training and support of LABBASE:
  a multi-disciplinary LIMS (Laboratory Information Management System)
  coded in Paradox and WordBasic.
  It co-operated with a legacy AS/400 appliction written in RPG/400 and CL,
  which i also maintained.
  During this project I managed two other programmers, the AS/400 administrator and a
  tech support person.
\end{position}


\title{ Principal }
\location{ Edmonton, Canada}
\dates{1990 to 1995}
\employer{Sapient Systems}
\begin{position}
Sapient Systems specialized in the creation of desktop database apps, including:
\begin{itemize}
\item {\it FastEDI} written in PAL (the Paradox Application Language) which
	provided a subset of the
	ANSI X.12 (V3.020) Electronic Data Interchange system for an
	oilfield supply company interested in easing the ordering process for
	the many regional offices of their large clients in the oil patch.
	{\it FastEDI v1.0} implemented
	the transaction sets for Price/Sales Catalog (832) and
	Purchase Order (850) thus enabling the electronic distribution
	of the latest pricelist and placement of orders.
\end{itemize}
\end{position}


\end{resume}
\end{document}
