
\title{ Principal }
\location{Edmonton, AB}
\employer{ \href{http://smurp.com}{smurp.com} }
\dates{2002 to 2011}

\begin{position}
Smurp.com provided contract programming and consulting services with a focus
on database-backed web sites and complex data processing operations.

\begin{itemize}
%  \item Nooron --- an experimental knowledge publishing and collaboration
%    environment featuring knowledge-based web-apps such as:
%    project management, pattern languages, blogging and FAQs.
%    It published knowledge within and about itself in various textual
%    and graphical forms:
%    DocBook, Rich Text, SVG, GIF, JPG, PDF and Postscript;
%    UML diagrams; state-transition diagrams; network graphs;
%    inheritance trees and PERT charts.

  \item PyOKBC --- A Python implementation of the
     \emph{Open KnowledgeBase Connectivity}
  system of knowledge representation and abstraction.
  It was designed to provide a single consistent interface to diverse structured
  information sources, to include ontologies, relational databases,
  xml documents, and topic maps. % PyOKBC was Free Software under the LGPL.

  \item PyRETS --- An implementation of the \emph{Real Estate Transaction System}
  for keeping the Vancouver Real Estate Board synchronized with MLS.ca

  \item CatPub --- A database publishing technology consisting of a
  Postscript templating system over a relational database back-end.
  Suitable for automatically preparing complex, highly customized,
  Postscript and PDF publications such as directories and catalogs,
  it is closed source software created under contract for a firm
  providing publishing services to the real estate industry.
  It is producing on the order of 10 thousand unique catalog pages
  every day containing constantly changing data for the largest
  real estate boards in Western Canada.

  \item TKQ2.0 --- A Django e-store system vending e-books for hundreds
  of educational publishers, through a dozen store-fronts, with sophisticated
  features such as promotions, steganographic watermarking in PDF, bundling,
  coupons and more.

  \item TKQW --- A Medusa-based ``digital drop-shipping`` system
  enabling digital goods sale and delivery by untrusted 3rd parties.

  \item ModelViz --- Added dynamic SVG-based touring facilities to this Django
  model entity-relationship visualizer.

  \item Alberta Lodging Association --- A Django-based lodgings database
  backing a web site, a printed directory and an associated advertising
  sales and layout system.

\end{itemize}

\end{position}
